TacticToe: Learning the Game of Tactics

### 2018-01-28 tactictoe_jv.tex
predictions: wip

\begin{definition}(Dependencies of tactic-goal pairs)\\
Let $\mathfrak{F}$ be the set of recorded tactic-goal pairs.
The dependencies $D_\infty$ of a tactic-goal pair $(t_0,g_0)$ is 
inductively defined by:

@@

\begin{definition}(Dependencies of a theorem)\\
Let $\mathfrak{T}$ be the set of recorded theorems.
The dependencies of a theorem $t$ are the set of theorems in 
$\mathfrak{T}$ appearing in the proof of $t$ as recorded in 
\cite{hh4h4}.\todo{cite}
Contrarily to the dependency relation in tactic-goal pairs, this relation is 
not a transitive closure.
\end{definition}

>>>>

\begin{definition}(Dependencies of a tactic-goal pair)\\
Let $\mathfrak{F}$ be the set of recorded tactic-goal pairs.
The dependencies $D_\infty$ of a tactic-goal pair $(t_0,g_0)$ is 
inductively defined by:

@@

\begin{definition}(Dependencies of a theorem)\\
Let $\mathfrak{T}$ be the set of recorded theorems.
The dependencies of a theorem $t$ are the set of theorems in 
$\mathfrak{T}$ appearing in the proof of $t$ as recorded in 
\cite{hh4h4}.\todo{cite} 
\end{definition}

\begin{remark}
We can note that the relation chosen for tactic-goal pairs is a transitive 
closure, which is not the case for theorem dependencies.
\end{remark}
